% !TEX TS-program = xelatex
% !TEX root = ../Thesis_Guo2013.tex
% !Mode:: "TeX:UTF-8"

This thesis and completing my bachelor's degree would not be possible without the support, assistance and advice of many people. And I would like to take this opportunity to acknowledge my family, friends, classmates and teachers who have helped me so much along the way.

First, I would like to thank my advisor, \textit{Dr.~Tao Zhou}, for guiding me through my undergraduate research. I remember how I walked to his lab during a group meeting and I was at that time a kid knowing nothing about research. Tao taught me how to focus on a problem, and how to break it down to smaller parts with better formulation and meanwhile seeking many ways to solve it. I greatly appreciate his encouragement, helpfulness and his easy-going style with students and lab members. I am also indebted to Tao for his generous recommendation for my academic visiting and applying to graduate schools. I would cherish my memories spent with Tao and other members in the Web Sciences Center.

I would also like to thank my teachers as I learned to reflect and grow up due to their influence. \textit{Mr.~Heping Pu} led me into mathematical analysis, the first math course in college. I learned how to transit from high school trick-playing to a new way of thinking in college from his inspiration and I respect his true dedication to teaching and education. I am also indebted to \textit{Mr.~Baohua Teng} for his encouragement and long discussions with him outside class. Among others, I enjoyed a lot in the quantum mechanics course taught by \textit{Mr.~Haitang Yang}, whose dedication, frankness and insight made him a charming physicist that I truly admire. 

For this thesis, I would like to thank \textit{Chenmin Sun}, my high school classmate, for talking with me over a math conclusion, and two users \textit{Alfred Chern} and \textit{Did} on math.StackExchange for helping me out of stuck. 

Then, I want to thank my friends and fellow classmates, who let me know I am never walking alone. 

Finally, I want to express my deepest thanks to my parents for their unconditional love and support. This thesis is dedicated to them. 